\documentclass{article}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage[margin=1in]{geometry}

\title{Rollout Depth Sweep Design}
\author{}
\date{}

\begin{document}
\maketitle

\section{Design}
The rollout depth sweep evaluates how increasing search depth in the sampled
best-response heuristic affects performance. Each depth value controls how many
successive seasons are simulated when scoring candidate joint actions. Deeper
rollouts increase computation but can improve decision quality by propagating
value estimates across multiple plies.

\subsection{Sweep Parameters}
We define a set of rollout depths $D = \{1, 2, 3\}$ and run a fixed number of
independent games per depth. All other parameters (rollout limit, discount,
unit weights, opponent sampling, and game length) remain fixed to isolate the
impact of rollout depth. The sweep is restricted to the negotiation powers only:
the heuristic policy is applied exclusively to the negotiation powers and all
non-negotiation powers remain as random baselines to preserve comparability.

\subsection{Procedure}
For each depth $d \in D$:
\begin{enumerate}
    \item Initialize a standard board and assign heuristic agents only to the
    negotiation powers; all remaining powers are random baselines.
    \item Run $G$ games of length $R$ rounds using the sampled best-response
    policy configured with rollout depth $d$.
    \item Record final supply center counts per power and compute the mean across
    the $G$ games.
\end{enumerate}

\subsection{Metrics}
We report (i) per-power average supply centers, (ii) the mean supply centers for
heuristic-controlled powers, and (iii) the mean supply centers for random
powers. These metrics allow comparison of absolute performance and relative
advantage over baselines.

\subsection{Reproducibility}
Each sweep uses a shared base seed so that each depth level samples the same
sequence of game seeds. This ensures differences arise from the rollout depth
rather than stochastic sampling variance.

\section{Results}
Table~\ref{tab:rollout-depth-results} reports the average supply centers for
each rollout depth. If results have not yet been collected, leave the table as
``TBD'' and populate after running the sweep.

\begin{table}[h]
    \centering
    \caption{Average supply centers by rollout depth (TBD).}
    \label{tab:rollout-depth-results}
    \begin{tabular}{@{}lccc@{}}
        \toprule
        \textbf{Depth} & \textbf{Heuristic Avg} & \textbf{Random Avg} & \textbf{Notes} \\
        \midrule
        1 & TBD & TBD & \\
        2 & TBD & TBD & \\
        3 & TBD & TBD & \\
        \bottomrule
    \end{tabular}
\end{table}

\end{document}
